---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unam.theme

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

The goal of unam.theme is to provide a ggplot2 theme using UNAM's graphic identity.

_Academic/Non-commercial use only._

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alberto-mateos-mo/unam.theme")
```
## Example

The custom theme and scales are used as follows:

```{r example, warning=FALSE}
library(unam.theme)
library(ggplot2)

ggplot(iris)+
  geom_point(aes(x = Sepal.Length, y = Petal.Length, colour = Species), size = 3)+
  scale_colour_unam()+
  theme_unam()
```

Using secondary palette:

```{r, warning=FALSE}
library(unam.theme)
library(ggplot2)

ggplot(iris)+
  geom_point(aes(x = Sepal.Length, y = Petal.Length, colour = Species), size = 3)+
  scale_colour_unam(palette = "secondary")+
  theme_unam()
```

Using a continuous scale:

```{r, warning=FALSE}
library(unam.theme)
library(ggplot2)

ggplot(iris)+
  geom_point(aes(x = Sepal.Length, y = Petal.Length, colour = Petal.Width), size = 3)+
  scale_colour_unam(palette = "basic", discrete = FALSE)+
  theme_unam()
```

Note: UNAM's graphic image consists of at most three colours: #003D79, #D59F0F and #B6985E, additional colours were selected using [colormind.io](http://colormind.io/) site.
